Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-03-18 bbbq_article.tex
Moved section 'Interesting haplotype for SARS-CoV-2' to discussion
Discussion starts making sense

% \paragraph{Does MHC-I present TMH-derived epitopes from pathogens as often?}

It is important that MHC-I presents both the peptides of the 
(healthy) cell, as well as possible pathogen-derived peptides when the
cell is infected. As described above, MHC-I presents TMH-derived epitopes 
from the human host more often. It is unknown if MHC-I has the same
dedication to present epitopes that stem from TMHs derived from
proteins produced by pathogen, either would the pathogen
be a virus or 
a bacterium.

@@

If presentation of TMHs on MHC-I would bring an evolutionary advantage 
in the recognition of pathogens by the immune system, 
it would follow that this is equally important for MHC-II, 
especially as the help of CD4+ T cells is needed for a long lasting CD8+ T cell 
response (\cite{novy2007cd4}). 
The mechanism to detect foreign TMHs by MHC-II would be unknown, 
similar to the discovery that MHC-I presents TMHs.

% \paragraph{Does MHC-II present TMH-derived epitopes from pathogens as often?}

It is unknown if MHC-II, like MHC-I, 
presents TMH-derived epitopes as often, either 
in humans,
bacteria or viruses.

@@

% \paragraph{Use of protein data in phylogenetics}

When using DNA sequences, one can use a skewed rate
in non- versus synonymous mutation
to detect the signature of selection (\cite{murrell2015gene}).
Using AA sequences, however, has its advantages,
as its is closer to the actual phenotype
selection acts upon: DNA may never be transcribed to RNA,
or its RNA may never be translated (\cite{diz2012proteomics}).
When using a proteome in phylogenetic research,
we know that the majority of proteins are selected to just
maintain their function most of the time, where
is the time spans there is selection, only a few AAs
can actually increase the 'fitness' of the
protein (\cite{anisimova2009investigating}).
There, when generalizing the dynamics of mostly purifying selection (to maintain
a protein's function) and a short duration of positive selection,
those genes that are selected cannot be detected (\cite{yang2000statistical}).

[RJCB: that was the last paragraph I ruthlessly moved
from introduction to here, as was suggested by GVDB]

We assume that epitopes 
derived from TMHs are actually presented by MHC-I and MHC-II.
Our analysis (at subsection \ref{subsec:elution_studies}) 
finds that 1.4\% (for MHC-I) and 4.0% (for MHC-II) 
of the epitopes presented 
overlap with a TMH.
It is unsure if this a true finding or a false positive.
One source of noise would stem from imperfect predictions
by the topology prediction software used. 
We have counteracted this by using two different topology prediction
software and confirm these have similar results.
Two biological sources of noise [GVDB: What do you mean by noise?]
are defective ribosomal products (DRiPs) (\cite{yewdell1996defective}) 
and peptide fusion \cite{delong2016pathogenic},
two processes that both result in peptide fragments
that did not originate from genome directly.
Note however, that both elution studies have a
methodological bias caused by mass spectronomy,
as hydrophobic fragments are detected less 
by mass spectronomy.

\subsection{\% epitopes overlapping with TMHs}

>>>>

% \paragraph{General}

Our understanding of the immune system and epitope prediction is 
important to fight disease. By this paper, we suggest that epitopes
derived from TMHs are needlessly overlooked and may inspire to investigate
new potential targets for combating pathogens.

% \paragraph{TMH presentation in vivo}

From elution studies and in silico predictions, 
we suggest that TMH-derived epitopes are presented in vivo.
The biochemical intracellular pathway to achieve this,
however, is still unknown.

An additional unknown is, although our findings are robust,
whether this is a false positive,
due to additive methodological artifacts.
An obvious artifact is that the elution studies used 
will contain some unavoidable sequencing errors.
Additionally, we assume that the epitopes naturally presented
are derived from a cleanly translated proteome.
Two known biological phenomena that violate this assumption
are defective ribosomal products (DRiPs) (\cite{yewdell1996defective}) 
and peptide fusion (\cite{delong2016pathogenic}),
two processes that both result in peptide fragments
that did not originate from genome directly.
Also, the TMH prediction software is imperfect.
This imperfection, however, appears to be of limited importance,
as two different topology prediction software have similar results.
Although those a couple of percent of epitopes that 
can be mapped directly to the proteome,
there is methodological bias caused by mass spectronomy,
as hydrophobic fragments are detected less 
by mass spectronomy. This means that the number of TMH-derived epitopes
is underestimated.
in vivo work in the lab will be needed to resolve this finding.

\subsection{Presentation of epitopes derived from TMHs}

@@

This study predict that TMH-derived epitopes are over-presented
in MHC-II as well. 
The intracellular pathway of MHC-II differs from that of MHC-I,
as it acquires epitopes from the exterior of the cell by phagocytosis.
How TMHs derived from exterior TMPs are lysed and loaded onto MHC-II 
is unknown. in vivo work is needed to elucidate this novel pathway.

% \paragraph{Immunogenicity}

In this study, we find that TMH-derived epitopes are over-presented.
The presentation of an epitope, however, 
is only a first step of an adaptive immune response.
We assume that the presentation of epitopes is
correlated with evoking a full immune response.
TMH-derived epitopes, however, are more hydrophobic than the average
epitope. If this evokes a stronger or weaker immune response is unknown,
and in vivo work is needed to resolve this.

\subsection{Evolutionary conservation of TMHs}

@@
